HPC--101\\Onboarding

### 2016-01-21 hpc_101/paper.tex
Updated the layout image.  Changed the description of how priorities are assigned, so that it just lists potential factors

\subsubsection{Layout}
\begin{frame}
	\frametitle{{\craycs} -- Layout}
	\includegraphics[width=0.95\textwidth]{images/high_level}
\end{frame}

@@

\begin{frame}
	\frametitle{What is a Job Scheduler?}
	Basic features expected of a job scheduler include:
	\begin{itemize}\footnotesize
        \item The capability to control and prioritize the execution order of unrelated jobs
        \item Allocates exclusive and/or non-exclusive access to resources to users for some duration of time so they can perform work
				\item Provides a framework for starting, executing, and monitoring work on the set of allocated nodes
				\item Arbitrate contention for resources by managing a queue of pending work
	\end{itemize}
	\bigskip
	For the {\craycs}, we utilize the \textbf{S}imple \textbf{L}inux \textbf{U}tility \textbf{R}esource \textbf{M}anager~\\ or simply known as the \emph{SLURM scheduler}
	\numlessfootnotetxt{\tiny \url{https://en.wikipedia.org/wiki/Job_scheduler}}
	\numlessfootnotetxt{\tiny \url{https://en.wikipedia.org/wiki/Slurm_Workload_Manager}}
	\numlessfootnotetxt{\tiny \url{http://slurm.schedmd.com/slurm.html}}
\end{frame}

\subsection{SLURM}
\begin{frame}
\frametitle{SLURM}
\begin{block}{How are jobs scheduled?}
User submitted jobs are assigned a priority using a fairshare algorithm.  Factors such as: runtime, resource usage request, age of job, and amount of compute time a user has used in recent history are all factored in to assigning a priority to a give job   
\end{block}
\end{frame}

>>>>

\subsubsection{Layout}
\begin{frame}
	\frametitle{{\craycs} -- Layout}
	\includegraphics[width=1\textwidth]{images/layout}
\end{frame}

@@

\begin{frame}
	\frametitle{What is a Job Scheduler?}
	Basic features expected of a job scheduler include:
	\begin{itemize}\footnotesize
        \item The capability to control and prioritize the execution order of unrelated jobs
        \item Allocate exclusive and/or non-exclusive access to resources to users for some duration of time so they can perform work
	\item Provides a framework for starting, executing, and monitoring work on the set of allocated resources
	\item Arbitrate contention for resources by managing a queue of pending work
	\end{itemize}
	\bigskip
	For the {\craycs}, we utilize the \textbf{S}imple \textbf{L}inux \textbf{U}tility \textbf{R}esource \textbf{M}anager~\\ or simply known as the \emph{SLURM scheduler}
	\numlessfootnotetxt{\tiny \url{https://en.wikipedia.org/wiki/Slurm_Workload_Manager}}
	\numlessfootnotetxt{\tiny \url{http://slurm.schedmd.com/slurm.html}}
\end{frame}

\subsection{SLURM}
\begin{frame}
\frametitle{SLURM}
\begin{block}{How are jobs scheduled?}
User submitted jobs are assigned a priority using a fairshare algorithm.\\
Factors such as the following are all used to assign a priority to a given job: 
\begin{itemize}
\item Runtime
\item Resource usage request
\item Age of job
\item Amount of core hours a user has used in recent history
\end{itemize}

\end{block}
\end{frame}
